---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Modeling two-choice decision behavior in R

<!-- badges: start -->
<!-- badges: end -->

See [Suthaharan, P., Corlett, P.R., & Ang, Y.S. (2021). Computational modeling of behavioral tasks: An illustration on a classic reinforcement learning paradigm]() for more detail.

Questions? Contact Praveen Suthaharan (praveen.suthaharan@yale.edu).

—————

The goal of *twochoiceRL* is to guide users on how to simulate two-choice decision behavior and, subsequently, to estimate (or recover) the behavioral parameters used to simulate the behavior.

## Installation

<!-- You can install the released version of twochoiceRL from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("twochoiceRL") -->
<!-- ``` -->


You can install the development version of *twochoiceRL* from [GitHub](https://github.com/psuthaharan/twochoiceRL) with:

``` r
# install.packages("devtools")
devtools::install_github("psuthaharan/twochoiceRL")
```
## Simulation

Simulate behavior:

```{r data, message=FALSE, results='hide'}
library(twochoiceRL)
# generate 100 individuals
# dataset1 contains behavioral data keeping only those selected-choice trials
dataset1 <- simulate_twochoiceRL(n_subj = 100, n_tr = 200, trials_unique = TRUE)

# dataset2 contains behavioral data keeping all trials (selected-choice and the non-selected-choice)
dataset2 <- simulate_twochoiceRL(n_subj = 100, n_tr = 200, trials_unique = FALSE)
```


## Visualization

Plot behavior:

```{r plot, message=FALSE}
# for plotting purpose - let's use dataset2
# You randomly select a participant to observe his/her behavior

# View first 10 rows of individual 100's data
head(dataset2$twochoiceRL[[100]],10)


# Visualize behavior 
p1 <- plot_twochoiceRL(data = dataset2, subj = 100, colors = c("#009999","#0000FF"))

# View expected value AND choice probability
p1[[3]]

# Visualize choice probability - animated 
plot_twochoiceRL(data = dataset2, subj = 100, colors = c("#009999","#0000FF"), plot_type = "animate")


```


## Estimation

Estimate behavioral parameters from simulated data:
  
```{r estimation, message=FALSE, results='hide'}
# Run MLE (elapsed time: ~ 5 min)
est_mle <- estimate_twochoiceRL(data = dataset1,
                                method = "mle",
                                plot = TRUE)
est_mle[[4]] # return MLE-estimation plot

# Run MAP (elapsed time: ~ 5 min)
est_map <- estimate_twochoiceRL(data = dataset1,
                                method = "map",
                                prior_mean = c(0,0),
                                prior_sd = c(5,5),
                                plot = TRUE)
est_map[[4]] # return MAP-estimation plot

# Run EML (elapsed time: ~ 1.4 hours)
est_eml <- estimate_twochoiceRL(data = dataset1,
                                method = "eml",
                                prior_mean = c(0,0),
                                prior_sd = c(5,5),
                                plot = TRUE)
est_eml[[4]] # return EML-estimation plot
```


Visualize the posterior hyperparameters per EML-iteration:
  
```{r hyperparameters}
# Laplace-approximated posterior hyperparameters
# for x1 AND x2
est_eml[[7]]

# x1, animated
est_eml[[8]]
```

